---
output: github_document
---
  
<!-- README.md is generated from README.Rmd. Please edit that file -->
  
[![Project Status: Wip - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/0.1.0/wip.svg)](http://www.repostatus.org/#wip)
[![Linux Build Status](https://travis-ci.org/PeteHaitch/MethylationTuples.svg?branch=master)](https://travis-ci.org/PeteHaitch/MethylationTuples)
[![Coverage Status](https://img.shields.io/codecov/c/github/PeteHaitch/MethylationTuples/master.svg)](https://codecov.io/github/PeteHaitch/MethylationTuples?branch=master)

<!-- TODO: Uncomment once in Bioc
[![Bioconductor downloads](http://bioconductor.org/shields/downloads/MethylationTuples.svg)](http://bioconductor.org/packages/stats/bioc/MethylationTuples.html) -->
<!-- TODO: Uncomment once obtained DOI
[![DOI](https://zenodo.org/badge/22085/PeteHaitch/MethylationTuples.svg)](https://zenodo.org/badge/latestdoi/22085/PeteHaitch/MethylationTuples) -->
<!-- TODO: Uncomment once in Bioc
[![Bioconductor devel build status](http://bioconductor.org/shields/build/devel/bioc/MethylationTuples.svg)](http://bioconductor.org/checkResults/devel/bioc-LATEST/MethylationTuples/) -->


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

R package: MethylationTuples
---

__MethylationTuples__ provides tools for analysing, managing, and visualising 
methylation patterns at genomic tuples.

## Installation

You can get the development version from GitHub. It depends on the 
[__DSArray__](www.github.com/PeteHaitch/DSArray).

```{r eval = FALSE}
devtools::install_github("PeteHaitch/DSArray")
devtools::install_github("PeteHaitch/MethylationTuples")
```

## What the hell do I do with this?

__MethylationTuples__ was initially developed to work hand-in-hand with 
[__methtuple__](www.github.com/PeteHaitch/methtuple) to analyse counts of DNA 
methylation patterns at tuples of genomic loci. In particular, I developed 
__methtuple__ and __MethylationTuples__ to analyse the _co-methylation_ of CpGs 
that exist on the same DNA fragment.

__TODO:__ Expand upon this and what __MethylationTuples__ has become

## Quick demo

__TODO__

## Have a feature request, need help, or want to get involved?

Code contributions, bug reports (and fixes!), and feature requests are most 
welcome. Please make any pull requests against the master branch at [https://github.com/PeteHaitch/MethylationTuples](https://github.com/PeteHaitch/MethylationTuples) 
and file issues at 
[https://github.com/PeteHaitch/MethylationTuples/issues](https://github.com/PeteHaitch/MethylationTuples/issues)
